---
title: 'Art Investing: First Insights from a data set with >228k art pieces'
author: 'Jens Laufer'
date: '10 3 2021'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

```{r}
source("R/data.R")
source("R/vis.R")
```



A few weeks ago I started my ["Artventure"]() of investing in physical art pieces. As a software/machinelearning engineer and data analyst I want to follow a data driven approach, although I am sure that my journey won't be just dead-dry analysis as art is pure emotion. To get the answers for my [questions]() I needed data, which I found on the website [Expresso Beans](https://expressobeans.com). The website is an art collector's community resource built and maintained by a volunteer staff. Although the design of the website is old-fashioned, it's a gold mine for art pieces. Thanks to the community for this excellent website.

To gain insights from the data with a analyst's toolset I developed a web scraper in Python which pumped the data into a MongoDB database. From the database I was able to a first exploratory data analysis (EDA) with the help of R, which I like more for data analysis than Python.

In these article I want to share my results of the first analysis. In case you are interested in the data set you can send me [message](mailto:jens@artventure.com).

### Overall overview


### Which variable describe the art pieces?